Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

\subsection{Daniel A. Smith and Max Van Kleek}

Daniel and Max are postdoctoral researchers on the SOCIAM project at the University of Southampton, and the principal architects of the WebBox
personal information store. They have research interests in HCI, the Semantic Web and Personal Information Management.

\subsection{Nigel R. Shadbolt}

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, at the University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and the Web Foundation.  He and Sir Tim Berners-Lee were Information Advisors to the UK Government, which led to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government's midata programme.

>>>>

\emph{Daniel A. Smith} and \emph{Max Van Kleek} are postdoctoral researchers on the SOCIAM project at the University of Southampton, and the principal architects of the WebBox personal information store. They have research interests in HCI, the Semantic Web and Personal Information Management.

\emph{Nigel Shadbolt} (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. As a member of the Public Sector Transparency Board, Chair of the UK Government's midata programme, and Chairman and Co-Founder of the Open Data Institute, Nigel has led the effort towards assisting the NHS to begin the continual release of health-care related datasets.
